My title

### 2024-04-03 paper/paper.qmd
modify data cleaning for model purposes

This paper begins with an [Introduction] framing the impact of economic downturns on work hours. It is followed by the [Data] section detailing methodology and cleaning efforts. In the [Results], we analyze work hours and nonresponse rates, leading to the [Discussion] on labour market responses to crises, including the impact of COVID-19, and addressing ethical issues. We later acknowledge our paper's Limitations, suggest paths for Future Research, especially on enhancing response rates, and conclude with a synthesis of our insights. The [Appendix] provides further survey information.

@@

## Source Data
The data was downloaded and filtered for the selected variables from the selected data variables from GSS[^1]. The data cleaning was performed based on value definitions as defined in the GSS codebooks [@gssCodebook]. One of the variable names `response` is renamed to be more informative (@tbl-use-var).

For the analysis, we retrieved the following data as described in @tbl-use-var.

| Variable | New Name  | Description                   | Example |
|----------|-----------|-------------------------------|---------|
| ID_      | id        | Response ID                   | 1       |
| YEAR     | year      | Year of the Data Recorded     | 1977    |
| SEX      | sex       | Respondent's gender           | Female  |
| AGE      | age       | Respondent's age              | 25      |
| HEALTH   | health    | Respondents' health condition | Good    |
| PHYSHLTH | phys_days | Days of Respondents' physical health being not good   | 15      |
| MNTLHLTH | ment_days | Days of Respondents' mental health being not good     | 20      |
| DEPRESS  | depress   | Whether respondents have been told having depression  | Yes     |

@@

??? maybe include a table of non-response rate
```{r}
#| label: fig-nonresponse-rate
#| fig-cap: Nonresponse Rates
#| echo: false
#| warning: false
#| message: false

@@

# calculate the percentages
total_responses <- nrow(GSS)
non_response_rate <- no_response_data/total_responses
questions <- c("Physical Unwellness","Mental Unwellness","Depression Status")
non_response_data <- cbind(questions,non_response_rate)

@@

Some of the questions in the dataset are not included resulting no responses collected in certain years, while the other responses were collected. This fact requires extra attention when cleaning and handling since the number of available responses will decrease when additional variables are added. Hence, an additional sub set of the data that only includes counted days of mental and physical un-wellness in the past 30 days is also included for only speculating these two variables.

@@

```{r}
#| label: fig-demo-mental
#| fig-cap: Gender and Age of People Apprehended Visulization Year-Depended
#| fig-subcap: ["Gender","Age cohorts"]
#| layout-ncol: 2
#| echo: false
#| warning: false
#| message: false

@@

```{r}
#| label: fig-demo-physical
#| fig-cap: Gender and Age of People Apprehended Visulization Year-Depended22
#| fig-subcap: ["Gender","Age cohorts"]
#| layout-ncol: 2
#| echo: false
#| warning: false
#| message: false

@@

@@

#Modify depress status for visualization
analysis_data$depress <- as.character(analysis_data$depress)
analysis_data <- mutate(analysis_data,
               depress = case_when(
                 depress == "1" ~ "Yes",
                 depress == "2" ~ "No",
                 TRUE ~ depress
               )
            )

#Graph
analysis_data|>
  ggplot(aes(x = ment_days, y = phys_days, color = depress)) +
  geom_point() +
  geom_smooth(method = "lm") +
  theme_minimal() +
  labs(x = "Mental Unwellness", y = "Physical Unwellness", color = "Depress") +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom")
```
\break

>>>>

This paper begins with [Introduction] framing the impact of mental health on one's well being. The [Data] section details variables, methodology, and cleaning processes used for analyses. In [Model] section, a model is proposed for determining how individual's depression status and counted days of mental unwellness in the past 30 days impacts their counted days of physical unwellness in the past 30 days. [Results] section analyzes how demographic and other mental health related factors would affect physical health with model calculations.

? Still need to fix this part
[Discussion] section includes . We later acknowledge our paper's [Limitations], suggest paths for [Future Research], especially on enhancing response rates, and conclude with a synthesis of our insights. The [Appendix] provides further survey information.

@@

## Source Data
The data was downloaded and filtered for the selected variables from the selected data variables from GSS[^1]. The data cleaning was performed based on value definitions as defined in the GSS codebooks [@gssCodebook]. The variable names are renamed to be more informative (@tbl-use-var).

| Variable | New Name  | Description                   | Example |
|----------|-----------|-------------------------------|---------|
| ID_      | id        | Response ID                   | 1       |
| YEAR     | year      | Year of the Data Recorded     | 1977    |
| SEX      | sex       | Respondent's gender           | Female/2|
| AGE      | age       | Respondent's age              | 25      |
| HEALTH   | health    | Respondents' health condition | Good    |
| PHYSHLTH | phys_days | Days of Respondents' physical health being not good   | 15      |
| MNTLHLTH | ment_days | Days of Respondents' mental health being not good     | 20      |
| DEPRESS  | depress   | Whether respondents have been told having depression  | Yes/1   |

@@

```{r}
#| label: fig-nonresponse-rate
#| fig-cap: Nonresponse Rates
#| echo: false
#| warning: false
#| message: false

@@

# calculate the percentages
total_responses <- nrow(GSS)
non_response_rate <- no_response_data/total_responses 
non_response_rate <- round(non_response_rate,3)
questions <- c("Physical Unwellness","Mental Unwellness","Depression Status")
non_response_data <- cbind(questions,non_response_rate)

@@

As shown in @fig-nonresponse-rate, some of the questions in the dataset are not included resulting no responses collected in certain years due to the change in survey methodology. This fact requires extra attention when cleaning and handling since the number of available responses will decrease when additional variables are added. Hence, an additional sub set of the data that only includes counted days of mental and physical un-wellness in the past 30 days (@tbl-sub-vars) is also included for only speculating these two variables while keeping as many responses as possible.

@@

```{r}
#| label: fig-demo-mental
#| fig-cap: Female Participants from 20 to 59 Years Old are More likely to Experience Mental Unwellness 
#| fig-subcap: ["Gender","Age cohorts"]
#| layout-ncol: 2
#| echo: false
#| warning: false
#| message: false

@@

```{r}
#| label: fig-demo-physical
#| fig-cap: Female Participants from 20 to 59 Years Old are More likely to Experience Physical Unwellness 
#| fig-subcap: ["Gender","Age cohorts"]
#| layout-ncol: 2
#| echo: false
#| warning: false
#| message: false

@@

Include some research about female having trouble due to medical racism etc. and possible reason why these age cohorts are more likely to experience both physical and mental unwellness.

@@

#Graph
graph_data|>
  ggplot(aes(x = ment_days, y = phys_days, color = depress)) +
  geom_point() +
  geom_smooth(method = "lm") +
  theme_minimal() +
  labs(x = "Mental Unwellness", y = "Physical Unwellness", color = "Depress") +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom")
```
\break
